---
title: "Data basics"
output: 
  learnr::tutorial:
    progressive: true
    allow_skip: true
    df_print: default
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(tidyverse)
library(nycflights13)
tutorial_options(exercise.timelimit = 60)
```

## Welcome

This tutorial will teach you how to look at data with R, which is a software environment and programming language for data science. If you would like to install R on your computer, please take a moment to read the [setup instructions]().

In this tutorial, you will learn how to use R to inspect the contents of a data frame or tibble. Data frames and tibbles are R's structures for storing tabular data; if you inherit a tabular dataset in R, it will almost certainly come as one of these structures. Here, you will learn how to do three things with data frames and tibbles:

1. look at the contents of a data frame or tibble
2. open a help page that describes a data frame or tibble
3. identify the variables and their types in a tibble 

You will also meet in this tutorial `mpg` and `flights`, two datasets that appear frequently in R examples. 

The readings in this tutorial follow [_R for Data Science_](http://r4ds.had.co.nz/), sections 3.2 and 5.1. 

## Data frames

### What is a data frame?

R stores tabular data in two formats:

1. As data frames
2. As tibbles, which are a special type of data frame

A __data frame__ is a rectangular collection of variables (in the columns) and observations (in the rows). An example is the `mpg` data frame found in the ggplot2 package (aka `ggplot2::mpg`). The `mpg` data frame contains observations collected by the US Environmental Protection Agency on 38 models of cars. To see the `mpg` data frame, type `mpg` in the code chunk below and then click "Submit Answer."

```{r mpg-setup}
mpg <- as.data.frame(mpg)
```

```{r mpg, exercise = TRUE}

```

<div id="mpg-hint">
**Hint:** Type `mpg` and then click the blue button.
</div>

```{r mpg-check, echo = FALSE}
# checking code
```

### A note about mpg

Note that the code above worked because I've already loaded the ggplot2 package for you in this tutorial: `mpg` comes in that package. If you would like to look at `mpg` on your own computer, you will need to first load ggplot2. You can do that in two steps:

1. First, run `install.packages('ggplot2')` to install ggplot2 if you do not yet have it.
2. Then, load ggplot2 with the `library(ggplot2)` command
3. After that, you will be able to access any object in ggplot2 — including `mpg` — until you close R. 

### View()

You can examine the contents of any data frame or tibble in R by running its name as a command. However, what you see might be overwhelming. Often a data frame or tibble contains more information than R can display in a single screen. In this case, you can look at the contents in a separate window with the `View()` command, which begins with a capital V. To use it, pass view the name of the data frame to display by writing the name between the parentheses that follow `View()`, e.g. `View(mpg)`.

## Help pages

### How to open a help page

You can learn more about `mpg` by opening its help page. The help page will explain where the `mpg`dataset comes from and what each variable in `mpg` describes. To open the help page, type `?mpg` in the code chunk below and then click "Submit Answer".

```{r help, exercise = TRUE}

```

<div id="help-hint">
**Hint:** Type `?mpg` and then click the blue button.
</div>

```{r help-check, echo = FALSE}
# checking code
```

### ? syntax

You can use the same syntax to open a help page for any object that comes in R or one of its packages. To open an object's help page, type a `?` before the object's name and then run the command, as you did with `?mpg`. This technique works for more than just data frames: you can also look at the help pages of functions. 

Notice that objects created by you or your colleagues will not have a help page (unless you make one).

### Exercises

```{r exercises1, exercise = TRUE}

```

```{r quiz1, echo = FALSE}
quiz(caption = "Use the code chunk above to help answer these questions.",
  question("What does the `drv` variable of `mpg` describe?  Read the help for `?mpg` to find out.",
           answer("Whether or not the vehicle has driver side airbags"), 
           answer("Whether a car is automatic or manual transmission"),
           answer("The number of cylinders in the car's engine"),
           answer("Something else", correct = "`drv` describes the type of drivetrain in a car: front wheel drive, rear wheel drive, or four wheel drive."), 
           allow_retry = TRUE
  ),
  question("How many rows are in the data frame named `cars`?",
           answer("2"), 
           answer("25"),
           answer("50", correct = TRUE),
           answer("100"),
           incorrect = "Hint: R numbers the rows of a data frame when it displays the contents of a data frame. As a result, you can spot the number of rows in `cars` by examining `cars` in the code block above.", 
           allow_retry = TRUE
  ),
  question("How many columns are in the data frame named `cars`?",
           answer("1"), 
           answer("2", correct = TRUE),
           answer("4"),
           answer("more than four"),
           incorrect = "Hint: If you inspect the contents of `cars` in the code block above, it should be pretty easy to count the number of columns.", 
           allow_retry = TRUE
  )
)
```

## Tibbles

### What is a tibble?

Now let's look at a special type of data frame that you will encounter in R: the tibble.

The `flights` data frame in the nycflights13 package is an example of a tibble. `flights` describes every flight that departed from New York City in 2013. The data comes from the US [Bureau of Transportation Statistics](http://www.transtats.bts.gov/DatabaseInfo.asp?DB_ID=120&Link=0), and is documented in `?flights`.

Use the code chunk below to print the contents of `flights`.

```{r flights, exercise = TRUE}

```

<div id="flights-hint">
**Hint:** Type the name of the data frame that you want to print and then click the blue button. I've already loaded the nycflight13 package for you.
</div>

```{r flights-check}
# checking code
```

### The tibble display

You might notice that `flights` prints a little differently from `mpg`: `flights` shows only the first few rows of the data frame and only the columns that fit on one screen. (To see the whole dataset, you can run `View(flights)` which will open the dataset in a special viewer). `flights` prints differently because it's a __tibble__. Tibbles are data frames, but slightly tweaked to be more user-friendly. For now, you don't need to worry about the differences between tibbles and data frames that are not tibbles; we'll come back to tibbles in more detail in a later tutorial.

## Variable types

### Type codes
 
```{r flights3, exercise = TRUE, exercise.eval = TRUE}
flights
``` 
 
You might have noticed that r displays a row of three (or four) letter abbreviations under the column names in `flights`. These abbreviations describe the type of variable that is stored in each column of `flights`:

* `int` stands for integers.

* `dbl` stands for doubles, or real numbers.

* `chr` stands for character vectors, or strings.

* `dttm` stands for date-times (a date + a time).

There are three other common types of variables that aren't used in this dataset but are used in other datasets:

* `lgl` stands for logical, vectors that contain only `TRUE` or `FALSE`.

* `fctr` stands for factors, which R uses to represent categorical variables
  with fixed possible values.

* `date` stands for dates.

This row of variable types is unique to tibbles and is one of the ways that tibbles try to be more user-friendly than data frames.

### Test your knowledge

```{r quiz2, echo=FALSE}
question("Which types of variables does `flights` contain? Check all that apply.",
         type = "multiple",
         allow_retry = TRUE,
         incorrect = "Look a little closer at `flights`.",
         answer("integers", correct = TRUE),
         answer("doubles", correct = TRUE),
         answer("factors"),
         answer("characters", correct = TRUE),
         correct = "Great Job!"
)
```

### Congratulations

You've now met R's basic table structures, data frames and tibbles; and you have learned how to inspect their contents. When you are ready, go on to the next tutorial to begin visualizing your data.

