---
title: "Tutorial"
output: 
  learnr::tutorial:
    progressive: true
    allow_skip: true
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(dplyr)
options(tutorial.event_recorder = learnr:::debug_event_recorder)
tutorial_options(
  exercise.eval = FALSE,
  exercise.alert_color = "orange"
)
```


## Using globally set color

Done: 

+ `exercise.alert_color` in the setup chunck can be used to change the alert color. 

+ The output of the code is now inside the alert, formatted as code/table. 

+ There is a default message in the error output, it can be changed by `exercise.execution_error_message`

To do: 

+ Add a check that the colors set by the user is valid (we have a finite set of colors)

+ Document the colors available

To discuss: 

+ Should we allow custom colors? For example, we could have `exercise.alert_color_background = "#f5a67d"`

__Example__

The current tutorial uses the following call in the setup chunk:

```
tutorial_options(
  exercise.eval = FALSE,
  exercise.alert_color = "orange"
)
```

> Try typing errors in the chunks of this tutorial

> NB: the solution to all is `mtcars`

```{r car, exercise=TRUE, exercise.timelimit = 10}
list(
```

```{r car-solution}
mtcars
```

Example using a different `exercise.execution_error_message`

```
{r carbis, exercise=TRUE, exercise.execution_error_message = "Ouch!"}
```

```{r carbis, exercise=TRUE, exercise.execution_error_message = "Ouch!"}
list(
```

```{r carbis-solution}
mtcars
```

## Using locally set color 

Colors can also be set at the chunk level.

### red

```
{r car-red, exercise.alert_color = "red"}
```

```{r car-red, exercise.alert_color = "red", exercise=TRUE}
list(
```


```{r car-red-solution}
mtcars
```


### orange

`exercise.alert_color = "orange"`

```{r car-orange, exercise.alert_color = "orange", exercise=TRUE,  exercise.timelimit = 10}
list(
```


```{r car-orange-solution}
mtcars
```


### purple

`exercise.alert_color = "purple"`

```{r car-purple, exercise.alert_color = "purple", exercise=TRUE,  exercise.timelimit = 10}
list(
```


```{r car-purple-solution}
mtcars
```

### blue

`exercise.alert_color = "blue"`

```{r car-blue, exercise.alert_color = "blue", exercise=TRUE,  exercise.timelimit = 10}
list(
```


```{r car-blue-solution}
mtcars
```


### violet

`exercise.alert_color = "violet"`

```{r car-violet, exercise.alert_color = "violet", exercise=TRUE,  exercise.timelimit = 10}
list(
```


```{r car-violet-solution}
mtcars
```


### yellow

`exercise.alert_color = "yellow"`

```{r car-yellow, exercise.alert_color = "yellow", exercise=TRUE,  exercise.timelimit = 10}
list(
```


```{r car-yellow-solution}
mtcars
```

### pink

`exercise.alert_color = "pink"`

```{r car-pink, exercise.alert_color = "pink", exercise=TRUE,  exercise.timelimit = 10}
list(
```


```{r car-pink-solution}
mtcars
```

### green

`exercise.alert_color = "green"`

```{r car-green, exercise.alert_color = "green", exercise=TRUE, exercise.timelimit = 10}
list(
```


```{r car-green-solution}
mtcars
```

