---
title: "Tutorial"
output: 
  learnr::tutorial:
    progressive: true
    allow_skip: true
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(dplyr)
#options(tutorial.event_recorder = learnr:::debug_event_recorder)
tutorial_options(
  exercise.eval = FALSE,
  exercise.alert_color = "orange",
  exercise.gradethis_success_color = "pink",
  exercise.gradethis_info_color = "orange",
  exercise.gradethis_warning_color = "violet",
  exercise.gradethis_danger_color = "blue"
)
gradethis::gradethis_setup()
```

## Using globally set color

Done: 

+ The gradethis colors can be set using options: `exercise.gradethis_success_color`, `exercise.gradethis_info_color`, `exercise.gradethis_warning_color` and `exercise.gradethis_danger_color`

__Example__

The current tutorial uses the following call in the setup chunk:

```
tutorial_options(
  exercise.eval = FALSE,
  exercise.alert_color = "orange",
  exercise.gradethis_success_color = "pink",
  exercise.gradethis_info_color = "orange",
  exercise.gradethis_warning_color = "violet",
  exercise.gradethis_danger_color = "blue"
)
```

Enter `mtcars`

```{r mtcars, exercise = TRUE}

```

```{r mtcars-solution}
mtcars
```


```{r mtcars-check}
grade_result(
  fail_if(~identical(.result, cars), "This is the cars (not mtcars) dataset."),
  pass_if(~identical(.result, mtcars))
)
```

## Using locally set color

With the following chunk setup: 

```
{r mtcars2 exercise.gradethis_success_color = "red", ,exercise.gradethis_info_color = "violet", exercise.gradethis_warning_color = "blue", exercise.gradethis_danger_color = "green"}
```

Enter `mtcars`

```{r mtcars2, exercise = TRUE, exercise.gradethis_success_color = "red", ,exercise.gradethis_info_color = "violet", exercise.gradethis_warning_color = "blue", exercise.gradethis_danger_color = "green"}

```

```{r mtcars2-solution}
mtcars
```


```{r mtcars2-check }
grade_result(
  fail_if(~identical(.result, cars), "This is the cars (not mtcars) dataset."),
  pass_if(~identical(.result, mtcars))
)
```

