---
title: "Tutorial"
output: 
  learnr::tutorial:
    progressive: true
    allow_skip: true
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(dplyr)
#options(tutorial.event_recorder = learnr:::debug_event_recorder)
gradethis::gradethis_setup(
  exercise.eval = FALSE,
  exercise.alert_class = "alert-orange",
  exercise.success_class = "alert-pink",
  exercise.info_class = "alert-orange",
  exercise.warning_class = "alert-violet",
  exercise.danger_class = "alert-blue"
)

tutorial_options(
  exercise.submitted_feedback = TRUE,
  exercise.submitted_output = TRUE
)

```

## Using globally set color

Done: 

+ The gradethis colors can be set using options: `exercise.success_class`, `exercise.info_class`, `exercise.warning_class` and `exercise.danger_class`

__Example__

The current tutorial uses the following call in the setup chunk:

```
gradethis::gradethis_setup(
  exercise.eval = FALSE,
  exercise.alert_class = "alert-orange",
  exercise.success_class = "alert-pink",
  exercise.info_class = "alert-orange",
  exercise.warning_class = "alert-violet",
  exercise.danger_class = "alert-blue"
)
```

Enter `mtcars`

```{r mtcars, exercise = TRUE}

```

```{r mtcars-solution}
mtcars
```


```{r mtcars-check}
grade_result(
  fail_if(~identical(.result, cars), "This is the cars (not mtcars) dataset."),
  pass_if(~identical(.result, mtcars))
)
```

## Using locally set color

With the following chunk setup: 

```
{r mtcars2 exercise.success_class = "alert-red", ,exercise.info_class = "alert-violet", exercise.warning_class = "alert-blue", exercise.danger_class = "alert-green"}
```

Enter `mtcars`

```{r mtcars2, exercise = TRUE, exercise.success_class = "alert-red", ,exercise.info_class = "alert-violet", exercise.warning_class = "alert-blue", exercise.danger_class = "alert-green"}

```

```{r mtcars2-solution}
mtcars
```


```{r mtcars2-check }
grade_result(
  fail_if(~identical(.result, cars), "This is the cars (not mtcars) dataset."),
  pass_if(~identical(.result, mtcars))
)
```

## Toggle Feedback or code display

With the following chunk: 

```
{r mtcars3, exercise.submitted_feedback = TRUE, exercise.submitted_output = TRUE}
```

Enter `mtcars`

```{r mtcars3, exercise = TRUE, exercise.submitted_feedback = TRUE, exercise.submitted_output = TRUE}
airquality
```

```{r mtcars3-solution}
mtcars
```


```{r mtcars3-check }
grade_result(
  fail_if(~identical(.result, cars), "This is the cars (not mtcars) dataset."),
  pass_if(~identical(.result, mtcars))
)
```

With the following chunk: 

```
{r mtcars4, exercise.submitted_feedback = TRUE, exercise.submitted_output = FALSE}
```

Enter `mtcars`

```{r mtcars4, exercise = TRUE, exercise.submitted_feedback = TRUE, exercise.submitted_output = FALSE}
airquality
```

```{r mtcars4-solution}
mtcars
```


```{r mtcars4-check }
grade_result(
  fail_if(~identical(.result, cars), "This is the cars (not mtcars) dataset."),
  pass_if(~identical(.result, mtcars))
)
```

With the following chunk: 

```
{r mtcars5, exercise.submitted_feedback = FALSE, exercise.submitted_output = TRUE}
```

Enter `mtcars`

```{r mtcars5, exercise = TRUE, exercise.submitted_feedback = FALSE, exercise.submitted_output = TRUE}
airquality
```

```{r mtcars5-solution}
mtcars
```


```{r mtcars5-check }
grade_result(
  fail_if(~identical(.result, cars), "This is the cars (not mtcars) dataset."),
  pass_if(~identical(.result, mtcars))
)
```

With the following chunk: 

```
{r mtcars6, exercise.submitted_feedback = FALSE, exercise.submitted_output = FALSE}
```

Enter `mtcars`

```{r mtcars6, exercise = TRUE, exercise.submitted_feedback = FALSE, exercise.submitted_output = FALSE}
airquality
```

```{r mtcars6-solution}
mtcars
```


```{r mtcars6-check }
grade_result(
  fail_if(~identical(.result, cars), "This is the cars (not mtcars) dataset."),
  pass_if(~identical(.result, mtcars))
)
```

