---
title: "Tutorial"
output: 
  learnr::tutorial:
    progressive: true
    allow_skip: false
    language: 
      fr:
        button:
          runcode: Marcher
        text:
          quiz: Las série de questions
      en:
        button:
          continue: Go!
          runcode: Run!
          hint: Hint!
          hint_plural: Hints!
          hinttitle: Maybe this can help you...
          startover: Redo!
          questionsubmit: Let's See
          questiontryagain: Retry
        text:
          quiz: It's a Quiz!
      es:
        button:
          runcode: Ejecutar
          runcodetitle: "$t(button.runcode) — {{kbd}}"
        text:
          startover: Empezar de nuevo
          enginecap: "$t(text.code) {{engine}}"
          code: Código
          quiz: Examen
runtime: shiny_prerendered
---

```{r eval=FALSE, include=FALSE}
# write tutorial_es.json for example in YAML header
jsonlite::write_json(
  list(
    button = list(runcode = "Ejecutar"),
    text = list(startover = "Empezar de nuevo")
  ),
  path = "tutorial_es.json",
  auto_unbox = TRUE
)
```


```{r setup, include=FALSE}
library(learnr)
library(nycflights13)
options(tutorial.event_recorder = function(...) {
  message(capture.output(learnr:::debug_event_recorder(...))) 
})
tutorial_options(
  exercise.eval = FALSE, 
  exercise.checker = function(label, user_code, envir_result, ...)  {
    if (is.null(envir_result))
      list(message = "Bad code!",
           correct = FALSE)
    else
      list(message = "Nice job!", 
           correct = TRUE, 
           location = "append")
  }
)
```

## intro

This is the intro to the whole ball of wax.

```{r context="render"}
shiny::selectInput(
  "language", "Choose a Language", 
  choices = names(learnr:::i18n_translations())
)
```

```{r context="server"}
shiny::observeEvent(input$language, {
  session$sendCustomMessage("localize", list(language = input$language))
})
```


### flights

```{r filter, exercise=TRUE}
# filter the flights table to include only United and American flights
flights
```

```{r filter-hint-1}
filter(flights, ...)
```

```{r filter-hint-2}
filter(flights, UniqueCarrier=="AA")
```

```{r filter-hint-3}
filter(flights, UniqueCarrier=="AA" | UniqueCarrier=="UA")
```

### YouTube Video

![](https://www.youtube.com/watch?v=TJmNvfhLCoI)

### Vimeo Video

![](https://player.vimeo.com/video/76979871)


### in between 

In betwixt and in between.

### solution {style="margin-top: 50px;"}

```{r exercise1-setup}
library(dplyr)
nycflights <- nycflights13::flights
```

```{r exercise1, exercise=TRUE}
# Change the filter to select February rather than January
nycflights <- filter(nycflights, month == 1)
```

<div id="exercise1-hint">

This is the hint for the exercise which I just provided.

</div>


## Viewing Data

Modify this code so that it prints only the first 5 rows of the `mtcars` dataset:

```{r cars, exercise=TRUE, exercise.eval=TRUE, exercise.timelimit = 10}
head(mtcars, n = 5)
```


```{r cars-solution}
mtcars <- head(mtcars, n = 5)
print(mtcars)
mtcars <- head(mtcars, n = 5)
print(mtcars)
mtcars <- head(mtcars, n = 5)
print(mtcars)
```

```{r cars-code-check}
#
```

```{r cars-check}
#
```

<div style="margin-top: 10px;">&nbsp;</div>

Modify this plot to use the `cyl` variable rather than the `wt` variable:

```{r ggplot, exercise=TRUE, exercise.eval=TRUE, fig.width=8}
library(ggplot2)
qplot(mpg, cyl, data = mtcars)
```

```{r ggplot-check}
mtcars <- head(mtcars, n = 5)
mtcars
```

## dygraphs

Add a range selector to the following dygraph:

```{r dygraphs, exercise=TRUE}
library(dygraphs)
dygraph(ldeaths) 
```

## quiz


```{r letter-a, echo=FALSE}
question("What number is the letter A in the English alphabet?", allow_retry = TRUE,
  answer("8"),
  answer("14"),
  answer("1", correct = TRUE),
  answer("23")
)
```


```{r quiz1, echo=FALSE}
quiz(
  question("What number is the letter A in the *English* alphabet?",
    answer("8"),
    answer("14", message = "That's $x+ 1$ **insane!**"),
    answer("1", correct = TRUE, message = "Good job!"),
    answer("23")
  ),
  question("Where are you right now? (select ALL that apply)",
    answer("Planet Earth", correct = TRUE),
    answer("Pluto", message = "How could you think we are on Pluto?"),
    answer("At a computing device", correct = TRUE),
    answer("In the Milky Way", correct = TRUE),
    incorrect = "Incorrect. You're on Earth, in the Milky Way, at a computer.",
    allow_retry = TRUE,
    try_again_button = "Do Over"
  ),
  question(sprintf("Suppose $x = %s$. Choose the correct statement:", 42),
    answer(sprintf("$\\sqrt{x} = %d$", 42 + 1)),
    answer(sprintf("$x ^ 2 = %d$", 42^2), correct = TRUE),
    answer("$\\sin x = 1$")
  )
)
```

## diagnostics buglet

```{r diagnostics-comma, exercise=TRUE}
# a false 'unexpected comma' diagnostic was printed at the end of line 4 below
GapMinderPlot(
  LifeExpectency, 
  countries = c("Germany", "United States", "New Zealand", "China",
                 "India", "Japan"))
GapMinderPlot(LifeExpectency)
```

## for in

```{r diagnostics-for, exercise=TRUE}
for (i in seq(1,5)){
     x <- i
 }
```

