---
title: "Tutorial User State"
output: learnr::tutorial
tutorial:
  id: tutorial-user-state
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(gradethis)

knitr::opts_chunk$set(echo = FALSE)
# switch between "local" and "client" to verify that feedback and correct are removed
options(tutorial.storage = "client")
options(tutorial.event_recorder = learnr:::debug_event_recorder)
```


## Topic 1

The current state of your progress in this tutorial:

```{r tutorial-user-state, echo=TRUE, context = "server"}
output$tutorial_user_state <- renderPrint({
  cat("session$userData$tutorial_state:\n")
  str(reactiveValuesToList(learnr:::get_tutorial_state()))
})
```

```{r tutorial-user-state-ui}
verbatimTextOutput("tutorial_user_state")
```

### Exercise 

Write whatever R code you want. This isn't graded (but the tutorial state records your latest run).

```{r anything, exercise=TRUE}
runif(1)
```

Write the R code required to add two plus two. This is graded, so all submissions are recorded in the tutorial state until the first correct submission. Once a correct submission is received, the state is no longer updated.

```{r two-plus-two, exercise=TRUE}

```

```{r two-plus-two-check}
grade_this({
  pass_if_equal(4, "Good job!")
  fail("Not quite, try again.")
})
```


Questions are always recorded in the tutorial state.

```{r quiz}
quiz(
  question("Which package contains functions for installing other R packages?",
    answer("base"),
    answer("tools"),
    answer("utils", correct = TRUE),
    answer("codetools"),
    allow_retry = TRUE
  ),
  question("Which of the R packages listed below are used to create plots?",
    answer("lattice", correct = TRUE),
    answer("tools"),
    answer("stats"),
    answer("grid", correct = TRUE),
    allow_retry = TRUE
  )
)
```


## Storage

Using `` `r getOption("tutorial.storage", "auto")` `` storage.

```{r storage-ui}
actionButton("storage", "Get Storage")
h4("Storage")
verbatimTextOutput("storage")
h4("Submissions")
verbatimTextOutput("submissions")
```

```{r storage-server, context="server"}
objs <- reactive({
  input$storage
  learnr:::get_all_state_objects(session)
})
output$storage <- renderPrint({
  str(objs())
})
output$submissions <- renderPrint({
  str(learnr:::submissions_from_state_objects(objs()))
})
```
