---
title: "Learnr Remote Evaluator Tests"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(exercise.checker = function(...){
  library(gradethis)
  gradethis::grade_learnr(...)
})

# Setup a remote evaluator.
options(tutorial.external.host = "http://localhost:8080")
```

```{r setup-global-exercise, include=FALSE}
x <- 123
library(gradethis)
```


## Basics

```{r basics1, exercise=TRUE}
rnorm(1)
```

Should produce one random number

### Code that generates an error

```{r badcode, exercise=TRUE}
# Reference a variable that's not defined
a123
```

You should see a red box that says `object 'a123' not found`

### Invalid syntax

```{r syntax, exercise=TRUE}
asdf + ___1
```

You should see a red box that says `... unexpected input 3: 4: asdf + _ ^`

## Setup Chunks

### Global Setup

```{r global1, exercise=TRUE}
x
```

Should be `123`. Defined in the `setup-global-exercise` chunk.

### Local Setup

Test an exercise that has a matching `-setup` chunk.

```{r local1, exercise=TRUE}
y
```

```{r local1-setup}
y <- "abc"
```

`y` should be `"abc"`

### Local Setup #2

Test an exercise that names its setup chunk in the knitr parameters.

```{r local2, exercise=TRUE, exercise.setup="local2su"}
y
```

```{r local2su}
y <- 456
```

`y` should be `456`.

## Timeouts

### Default timeouts

By default, we set the timeout to 30s for remote evaluator requests. This request should timeout after 30-35s.

```{r timeout, exercise=TRUE}
Sys.sleep(35)
print("I didn't time out!")
```

You should see an error message stating that the exercise timed out.

### Option timeout

Using the option `options(tutorial.exercise.timelimit = 5)`

```{r optTimeout, exercise=TRUE}
# TODO
```

### Exercise-Specific Timeout

```{r exTimeout, exercise=TRUE, exercise.timelimit=5}
Sys.sleep(7)
print("I didn't timeout")
```

After 5-10 seconds, you should see an error message about the timeout being exceeded.

## Code Checkers

### Exercise-Specific Check

Enter the number 4, then click "Submit Answer" (**not Run Code**)
```{r excheck, exercise=TRUE}
3
#4
```
 
```{r excheck-check}
gradethis::grade_result(
  gradethis::fail_if(~ identical(.result, 1), "Custom message for value 1."),
  gradethis::pass_if(~ identical(.result, 2), "Custom message for value 2."),
  gradethis::fail_if(~ identical(.result, 3), "Custom message for value 3."),
  gradethis::pass_if(~ identical(.result %% 2, 0) && (.result < 5),
          "Even number below 5")
)
```

If you enter `3`, you should see an error: `Custom message for value 3.`. If you enter `4`, you should see a success message with praise.


### Checks that leverage setup blocks

Checks should be able to leverage the setup block to e.g. allow setup to call `library(gradethis)` and then have the checker use those functions without having to namespace them

The following should work just as the previous example did. Click "Submit Answer" (**not Run Code**)

```{r excheck2, exercise=TRUE}
3
#4
```
 
```{r excheck2-check}
grade_result(
  fail_if(~ identical(.result, 1), "Custom message for value 1."),
  pass_if(~ identical(.result, 2), "Custom message for value 2."),
  fail_if(~ identical(.result, 3), "Custom message for value 3."),
  pass_if(~ identical(.result %% 2, 0) && (.result < 5),
         "Even number below 5")
)
```

If you enter `3`, you should see an error: `Custom message for value 3.`. If you enter `4`, you should see a success message with praise.


