---
title: "Question Types in Learnr"
output:
  learnr::tutorial:
    allow_skip: true
runtime: shiny_prerendered
tutorial:
  # id: "com.example.tutorials.my-first-tutorial"
  version: 2.17
  # user_id: "barret"
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = TRUE, highlight = TRUE)
```


## Basic Types

There are three basic types of quiz questions: radio button, checkbox, and text box.  Each one allows for one choice, multiple choices, and direct user input respectively.

-------------------

### Radio

When wanting only one answer from a user, use a radio button question.  Even if multiple options are correct, the user is only able to pick a single value.  The `type` value supplied to a `question` should be `"radio"` or `"single"`.  If only one correct option is provided when `type = "auto"`, a radio button question will be produced.

```{r radio}
question(
  "Is this a good question?",
  answer("yes", correct = TRUE),
  answer("no", message = 'This is a good question.')
)
```

-------------------

### Checkbox

When wanting possibly **multiple** answers from a user, use a checkbox question.  All answers that are marked correct must be selected by the user to have the answer be correct.  A minimum of one correct answer is required.  The `type` value supplied to a `question` should be `"checkbox"` or `"multiple"`.  If more than one correct option is provided when `type = "auto"`, a checkbox question will be produced.

```{r checkbox}
question(
  "Select all the toppings that belong on a Margherita Pizza:",
  answer("tomato", correct = TRUE),
  answer("mozzarella", correct = TRUE),
  answer("basil", correct = TRUE),
  answer("extra virgin olive oil", correct = TRUE),
  answer("pepperoni", message = "Great topping! ... just not on a Margherita Pizza"),
  answer("onions"),
  answer("bacon"),
  answer("spinach"),
  random_answer_order = TRUE,
  allow_retry = TRUE,
  try_again = "Be sure to select all toppings!"
)
```

-------------------

### Text box

If you'd like users to submit open-ended answers, use a text box question.  Correct and incorrect answers will be matched exactly (including white space). A minimum of one correct answer is required.  The `type` value supplied to a `question` should be `"text"` to produce a text box question.

Text value inputs are trimmed before they are compared to answers provided.

```{r text_box}
question(
  "Please enter the word 'C0rrect' below:",
  answer("correct", message = "Don't forget to capitalize"),
  answer("c0rrect", message = "Don't forget to capitalize"),
  answer("Correct", message = "Is it really an 'o'?"),
  answer("C0rrect", correct = TRUE),
  type = "text",
  allow_retry = TRUE
)
```

-------------------

### Extra Arguments


* Messages
  * `correct`: Message to be displayed when a user gets a correct answer.
  * `incorrect`: Message to be displayed when a user gets an incorrect answer and is not able to try again.
  * `try_again`: Message to be displayed when a user gets an incorrect answer and has the ability to try again.
  * `message`: An additional, neutral message to be displayed along with the correct/incorrect message.
  * `post_message`: Additional message to display along with correct/incorrect feedback.  If `allow_retry` is `TRUE`, this message will only be displayed after the correct submission.  If `allow_retry` is `FALSE`, it will produce a second message alongside the `message` value.
* Question Setup
  * `allow_retry`: Boolean that determines if the user should get a second chance at submitting their answer
  * `random_answer_order`: Boolean that determines if the question answers are displayed in a random order
* Buttons
  * `submit_button`: Label of the submit button
  * `try_again_button`: Label of the submit button

Example:

```{r options, echo = TRUE}
question(
  "How many options are set in this question?",
  answer("1", message = "Really?"),
  answer("2"),
  answer("3"),
  answer("9", correct = TRUE, message = "Message for value: 9"),
  type = "auto", # radio
  correct = "Question is correct!",
  try_again = "Higher!",
  message = "Reminder to do something after answering the question...",
  post_message = "Message to be displayed after the correct answer is found",
  submit_button = "Submit Answer Here!",
  try_again_button = "Try Again Here!",
  allow_retry = TRUE,
  random_answer_order = TRUE
)
```

## Custom Questions

There are four methods used to define a custom question.  Each [s3 method](http://adv-r.had.co.nz/S3.html) should correspond to the `type = TYPE` supplied to the question.

* `question_initialize_input.TYPE(question, answer_input, ...)`
  * Determines how the question is initially displayed to the users. This should return an object that can be displayed using [`shiny::renderUI`](https://shiny.rstudio.com/reference/shiny/latest/renderUI.html).  This method will be re-executed if the question is attempted again.
* `question_completed_input.TYPE(question, ...)`
  * Determines how the question is displayed after a submission.  This should return an object that can be displayed using [`shiny::renderUI`](https://shiny.rstudio.com/reference/shiny/latest/renderUI.html).
* `question_is_valid.TYPE(question, answer_input, ...)`
  * This method should return a boolean that determines if the input answer is valid.  Depending on the value, this function enables and disables the submission button.
* `question_is_correct.TYPE(question, answer_input, ...)`
  * This method should return a boolean that determines if the input answer is correct.  This function's return value should be the output of `learnr::question_is_correct_value`.


#### **No Feedback**

Let's say we want a radio button question, but we want to handle how the question is displayed after a user submits their answer.
One option would be to leave a generic `"Thank you for your submission"` and provide no feedback to the user.

In the example below, we use a radio question as the base question type but handle the completed input stage using a `"no_feedback"` type value.
Since the stages of displaying a question are dispatched using s3 methods, we set the type to `type = c("no_feedback", "radio")` to utilize the radio button question stages for the stages without a `no_feedback` method implemented.

With the code being executed in a `shiny_prerendered` document, there are two execution phases: `"render"` and `"server"` execution.  Please see [https://rmarkdown.rstudio.com/authoring_shiny_prerendered.html](https://rmarkdown.rstudio.com/authoring_shiny_prerendered.html) for an indepth explaination of these phases.  For our purposes with `learnr`, we will use a `"server-start"` context to add our custom s3 method for the `"server"` phase. The `"server-start"` phase will be executed once for the `"server"` phase, not for every users visiting the tutorial.  To have the custom function be found, we must store it in the Global Environment by using the double arrow assignment.

````markdown
`r ''````{r no_feedback, context = "server-start"}
# assign to global env
question_completed_input.no_feedback <<- function(question, answer_input, ...) {
  # Return a generic message
  tagList(
    tags$label(class="control-label", question$question),
    tags$h3(question$feedback)
  )
}
```
````

This _non-standard_ setup above could be avoided if the s3 methods were `library`ed from a package in the `setup` code block.

```{r no_feedback, context = "server-start"}
# assign to global env
question_completed_input.no_feedback <<- function(question, answer_input, ...) {
  # Return a generic message
  tagList(
    tags$label(class="control-label", question$question),
    tags$h3(question$feedback)
  )
}
```

Example quiz question using the `"no_feedback"` question type.


```{r no_feedback_questions, echo = TRUE}
no_feedback_question <- function(..., feedback = "Thank you for your submission") {
  ques <- question(
    ...,
    type = c("no_feedback", "radio"),
    correct = NULL,
    incorrect = NULL
  )
  ques$feedback <- feedback
  ques
}

quiz(
  no_feedback_question(
    "Is this a good question?",
    answer("yes", correct = TRUE),
    answer("no")
  ),
  no_feedback_question(
    "Will you see which answer you submitted?",
    answer("yes"),
    answer("no", correct = TRUE),
    random_answer_order = TRUE,
    feedback = "Your answer has been submitted"
  )
)
```

-------------------

### Ignore White Space


Let's create one more custom example that maintains all whitespace for a text box submission.

This example should perform like a text box but maintain the white space before compairing it to the known answers.  To accomplish this, we will create a `question_is_correct.text_no_trim` method.  Remember, `question_is_correct` requires that the return value is generated from `question_is_correct_value`.


````markdown
`r ''````{r no_trim_whitespace, context = "server-start"}
# use double arrow to assign to global namespace
question_is_correct.text_no_trim <<- function(question, answer_input, ...) {

  # validate something is given
  if (is.null(answer_input) || nchar(answer_input) == 0) {
    showNotification("Please enter some text before submitting", type = "error")
    # use shiny's `req(NULL)` to stop execution
    req(NULL)
  }

  for (ans in question$answers) {
    if (identical(ans$option, answer_input)) {
      return(question_is_correct_value(
        ans$is_correct,
        ans$message
      ))
    }
  }
  # answer not found
  question_is_correct_value(FALSE, NULL)
}
```
````

```{r no_trim_whitespace, context = "server-start"}
# use double arrow to assign to global namespace
question_is_correct.text_no_trim <<- function(question, answer_input, ...) {

  # validate something is given
  if (is.null(answer_input) || nchar(answer_input) == 0) {
    showNotification("Please enter some text before submitting", type = "error")
    # use shiny's `req(NULL)` to stop execution
    req(NULL)
  }

  for (ans in question$answers) {
    if (identical(ans$option, answer_input)) {
      return(question_is_correct_value(
        ans$is_correct,
        ans$message
      ))
    }
  }
  # answer not found
  question_is_correct_value(FALSE, NULL)
}
```

```{r no_trim, echo = TRUE}
question(
  "Please enter the phrase '&nbsp;&nbsp;abc&nbsp;&nbsp;def&nbsp;&nbsp;&nbsp;' below:",
  answer("abc def", message = "There are two spaces in the middle"),
  answer("abc  def", message = "There are two spaces at the beginning"),
  answer(" abc  def", message = "There are two spaces at the beginning"),
  answer("  abc def", message = "There are spaces at the end"),
  answer("  abc def ", message = "more spaces at the end"),
  answer("  abc def  ", message = "even more spaces at the end"),
  answer("  abc  def   ", correct = TRUE),
  type = c("text_no_trim", "text"),
  allow_retry = TRUE
)
```
