---
title: "learnr Tutorial Examples"
description: >
  A collection of example interactive tutorials that use the learnr package.
toc: false
output:
  html_document:
    toc_float: false
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
source("example_cards.R", local = TRUE)
```

```{css echo=FALSE}
.row > main { max-width: 100%; }
```

## Complete Tutorials

These tutorials were designed to showcase the features of the learnr package --- and to teach learners how to use R!
Try working through these tutorials to get a sense of the look and feel of a learnr tutorial.
Then check out the source code to see how these tutorials were made!

```{r example-cards-showcase}
example_cards("examples.yml", "showcase")
```

## Demo Tutorials

There's a lot that learnr can do.
These tutorials showcase specific learnr features or show you some possibilities that build on other packages designed to work with R Markdown and learnr.

```{r example-cards-demo}
example_cards("examples.yml", "demo")
```

## Community Showcase

learnr's community has built some excellent tutorials and resources
for learning data science and programming.
Here are just a few highlights.
(Please [suggest your favorite learnr resources](https://github.com/rstudio/learnr/discussions/categories/show-and-tell).)

```{r example-cards-community}
example_cards("examples.yml", "community")
```

```{js echo=FALSE}
document.getElementById('main').classList = ''
```
