---
title: "learnr Tutorial Examples"
description: >
  A collection of example interactive tutorials that use the learnr package.
toc: false
output:
  html_document:
    toc_float: false
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
here <- function(...) {
  file.path(dirname(knitr::current_input(dir = TRUE)), ...)
}
source(here("example_cards.R"), local = TRUE)
```

```{css echo=FALSE}
.contents { max-width: 100%; }
```

## Complete Tutorials

These tutorials were designed to showcase the features of the learnr package —
and to teach learners how to use R!
Try working through these tutorials to get a sense of the look and feel of a learnr tutorial.
Then check out the source code to see how these tutorials were made!

```{r example-cards-showcase}
example_cards(here("examples.yml"), "showcase")
```

## Demo Tutorials

There's a lot that learnr can do.
These tutorials showcase specific learnr features
or show you some possibilities that build on other packages designed
to work with R Markdown and learnr.

```{r example-cards-demo}
example_cards(here("examples.yml"), "demo")
```
