---
title: "Tutorial"
output: 
  tutor::tutorial:
    theme: cerulean
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(tutor)
knitr::opts_chunk$set(echo = FALSE)
```

This is an interactive R tutorial. R code chunks can be made into exercises by adding the `exercise=TRUE` chunk option. By default, R code within exercise chunks is not pre-evaluated, however you can change this behavior using the `exercise.eval` chunk option.

Be sure to add a chunk label to all of your interactive chunks (e.g. `two-plus-two` and `add-function` in the sample exercises below). This provides a unique identifer for interactive components which is used for restoring progress, recording work, etc.

## Exercise 1

*Here's a simple exercise with an empty code chunk provided for entering the answer.*

Write the R code required to add two plus two:

```{r two-plus-two, exercise=TRUE}

```

## Exercise 2

*Here's an exercise with some prepopulated code as well as `exercise.lines = 5` to provide a bit more initial room to work.*

Now write a function that adds any two numbers and then call it:

```{r add-function, exercise=TRUE, exercise.lines = 5}
add <- function() {
  
}
```

## Exercise 3

*Here's an exercise where the chunk is pre-evaulated via the `exercise.eval` option (so the user can see the default output we'd like them to customize). We also add a "hint" to the correct solution via the chunk immediate below labeled `print-limit-hint`.*

Modify the following code to limit the number of rows printed to 5:

```{r print-limit, exercise=TRUE, exercise.eval=TRUE}
mtcars
```

```{r print-limit-hint}
head(mtcars)
```

## Quiz

*You can include any number of single or multiple choice questions as a quiz. Use the `question` function to define a question and the `quiz` function for grouping multiple questions together.*

Some questions to verify that you understand the purposes of various base and recommended R packages:

```{r quiz}
quiz(
  question("Which package contains functions for installing other R packages?",
    answer("base"),
    answer("tools"),
    answer("utils", correct = TRUE),
    answer("codetools")
  ),
  question("Which of the R packages listed below are used to create plots?",
    answer("lattice", correct = TRUE),
    answer("tools"),
    answer("stats"),
    answer("grid", correct = TRUE)
  )
)
```

